---
title: "Read Me"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

Quasi-explicit calibration of the modified SVI model. The optimization method follows Martini & Marco (2009), with some modificiation. 

The modified SVI function is:

$$ v(x) = [a + b(\rho(x-m)+\sqrt{(x-m)^2 + \sigma^2})]^H
$$

Given that the function has 6 parameters, and many local minimums, two-step quasi-explicit calibration method has some  advantages to find global optimal parameters. 

Read a sample chain (iv.csv, $\tau = 0.12$ ), and fit with the two-step optimization.

```{r}
library(dplyr)
library(ggplot2)
source('svi_h.R')
# read one sample ivs at tau = 0.12
tau = 0.12
c <- read.csv('iv.csv')
# measure estimation time
ptm <- proc.time()
param <- fit_ga_svi(c$k,c$iv,tau)
#show how long it takes for estimate the parameters
print(proc.time()-ptm)

print(param)
```

```{r}

# SVI parameterized IV estimation
c$svi <- svi_fun(c$k,as.numeric(param[1,2:7]))/sqrt(tau)

# plot fitting results
ggplot(c, aes(x = k, y = iv)) + geom_point()  + 
  geom_line(aes(y = svi), color = 'red')
```

```{r}
c$err = c$iv - c$svi

ggplot(c, aes(x = k, y = err)) + geom_point()
print(sd(c$err))
```

